method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added condition view for levator

@@

>>>>

# compute posthoc tests for within measures
EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")

EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

EMGCorrView_con <- cbind(EMGCorrView_con,
                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
                                                          df_error = EMGCorrView_con$df,
                                                          ci = 0.95),
                                                          digits = 2))

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

# levator

@@

# compute posthoc tests for within measures
EMGLevView_emm <- emmeans::emmeans(EMGLevView_aov$aov, specs = "block")

EMGLevView_con <- as.data.frame(pairs(EMGLevView_emm, adjust = "bonferroni"))

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

EMGLevView_con <- cbind(EMGLevView_con,
                         format(effectsize::t_to_eta2(t = EMGLevView_con$t.ratio,
                                                          df_error = EMGLevView_con$df,
                                                          ci = 0.95),
                                                          digits = 2))

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")
